---
title: "CS498 AML HW6"
author: "Pengyu Cheng"
date: "10/19/2018"
output:
  html_document: default
  pdf_document: default
---

# Question a): Regress house price (variable 14) against all others, and use leverage,
Cook’s distance, and standardized residuals to find possible outliers. Produce
a diagnostic plot that allows you to identify possible outliers
```{r}
library(data.table)
boston.data = fread('https://archive.ics.uci.edu/ml/machine-learning-databases/housing/housing.data')
head(boston.data)
model = lm(boston.data$V14~., data = boston.data)
plot(model)
```
From the "residual vs fitted" plot we can see there exists some non-linearity replationship and point 369, 372 and 373 are identified as possible outliers. We refer to "scale-location" for further information. In this plot, we find that points 373, 372 and 369 are indeed beyond 2 standard deviations;thus we feel comfortable to flag them as possible outliers. From the "residuals vs leverage" plot, we identify another point as possible outlier: point 365 with  suspiciously large Cook’s distance. There are points that have high leverage but small residuals and we leave it as it is for now.  

# Question b): Remove all the points you suspect as outliers, and compute a new regression. Produce a diagnostic plot that allows you to identify possible outliers.
```{r}
#remove data points 373, 369 365 and 372
new.boston.data = boston.data[-c(373, 372, 369, 365),]
new.model = lm(new.boston.data$V14~., data=new.boston.data)
plot(new.model)
```

# Question c): Apply a Box-Cox transformation to the dependent variable – what is the
best value of the parameter?
```{r}
library(MASS)
boxcox(new.model)
boxcox.transform = boxcox(new.model)
best.lambda = boxcox.transform$x[which(boxcox.transform$y == max(boxcox.transform$y))]
```
The best parameter of $\lambda$ is `r best.lambda`

# Question d): Now transform the dependent variable, build a linear regression, and check
the standardized residuals. If they look acceptable, produce a plot of fitted
house price against true house price.
```{r}

transform.model = lm(((new.boston.data$V14^best.lambda - 1)/best.lambda) ~., data=new.boston.data)
plot(transform.model)
plot(new.boston.data$V14, (fitted.values(transform.model) * best.lambda + 1)^(1/best.lambda))
```



